% -*-latex-*-
% 
% For questions, comments, concerns or complaints:
% thesis@mit.edu
% 
%
% $Log: cover.tex,v $
% Revision 1.9  2019/08/06 14:18:15  cmalin
% Replaced sample content with non-specific text.
%
% Revision 1.8  2008/05/13 15:02:15  jdreed
% Degree month is June, not May.  Added note about prevdegrees.
% Arthur Smith's title updated
%
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach

% NOTE:
% These templates make an effort to conform to the MIT Thesis specifications,
% however the specifications can change. We recommend that you verify the
% layout of your title page with your thesis advisor and/or the MIT 
% Libraries before printing your final copy.
\title{Efficient simulation of Large-Scale\\ Superconducting Nanowire Circuits}

\author{Tareq ``Torque'' El Dandachi}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\department{Department of Electrical Engineering and Computer Science}

% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}
\degree{Bachelor of Science in Computer Science and Engineering}

% As of the 2007-08 academic year, valid degree months are September, 
% February, or June.  The default is June.
\degreemonth{January}
\degreeyear{2023}
\thesisdate{January 27, 2023}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{\copyright IBM, 1990.  Do not open till Xmas.}

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Karl K. Berggren}{Professor of Electrical Engineering and Computer Science}

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Leslie A. Kolodziejski}{Professor of Electrical Engineering and Computer Science\\
Chair, Department Committee on Graduate Students}

% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle

% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.

%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.

% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}

% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}

\cleardoublepage

\section*{Acknowledgments}

I would like to extend my deepest gratitude to my friends and colleagues, who have been a constant source of support and inspiration throughout my research. Their unwavering encouragement and advice has helped fuel my passion for research and their belief in me was instrumental to my ability to complete this thesis. I’d especially like to thank:

My advisor, Professor Karl Berggren, who introduced me to superconducting nanowires, and whose advice and expertise guided me throughout. His guidance was instrumental in shaping my research and I am deeply grateful for the opportunity to be part of his lab. The Quantum Nanostructures and Nanofabrication (QNN) group will forever hold a special place in my heart.

Marco Colangelo, who taught me everything I know about the measurement and fabrication of superconducting devices. He has and always will be my role model, not only in his expertise and knowledge but also in his dedication and spirit. His invaluable advice, feedback, and support was instrumental in shaping my work and who I am. I am deeply grateful to have had him as a mentor and colleague.

Professor Stefan Krastanov, an exceptional educator and mentor, who introduced me to the field of simulation, the Julia programming language, and sparked my love for optimization. His support and advice was instrumental in my pursuit of research and I will forever appreciate having done research under your supervision.

Reed Foster, my partner in crime, who I had the pleasure of meeting during my undergraduate studies at MIT, taking multiple classes together, conducting undergraduate research and starting our masters studies together at QNN. The conversations we had in the shared undergraduate office and all our discussions on RF electronics, FPGAs and Julia will always hold a special place in my heart. I wish Reed all the best in his Ph.D. studies and hope our paths will cross again in the future.

Emma Batson and Adina Bechhofer, whom I’m lucky to call both friends and colleagues, for making the lab such a fun and enjoyable experience. Their indulgence of my love for optimization and theory made the research process so much more fulfilling.

Savoldy and Colin Greybosh, who listened to me obsess, complain and fall in love with my work every single day. 

Ayo Lindblad for all our lunches and chats that fueled my love for math.

And finally, to my dear friend, Ashika Verma, for always believing in me and pushing me to be a better person. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -*-latex-*-
